---
title: "rpdtls"
author: "Jun Inoue"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{rpdtls}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  
---
#purpose

This package aims to get the reproductive data of a dairy farm.

#a nesessary data frame

  1.Cows : DF

   | LineNo | Group | Stage | Cowcode | CowGroup | cowidNo | birthday | parity | calving_date | daysfrmcalving | AItimes | firstAI_date | fstAIdaysfrmcalving | lastAI_date | daysfrmlstAI | expDateofnextCalving | opendays | base_date|

   | LineNo | Group | Stage | 牛ｺｰﾄﾞ | 牛群 | 個体識別番号 | 生年月日 | 産次 | 分娩日 | 分娩後日数 | 授精回数 | 初回授精日 | 初回授精日数 | 最終授精日 | 授精後日数 | 分娩予定日 | 空胎日数 | 基準日 | 

  1. Heifers : DFH

   | LineNo | Group | Stage | Cowcode | CowGroup | cowidNo | birthday | parity | age_in_day | age_in_month | AItimes | firstAI_date | fstAI_age_in_month | lastAI_date | daysfrmlstAI | expDateofnextCalving | openmonths | base_date|

   | LineNo | Group | Stage | 牛ｺｰﾄﾞ | 牛群 | 個体識別番号 | 生年月日 | 産次 | 日齢 | 月齢 | 授精回数 | 初回授精日 | 初回授精月齢 | 最終授精日 | 授精後日数 | 分娩予定日 | 空胎月数 | 基準日 |
   
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(tidyverse)
library(readr)
library(rpdtls)
```

```{r ttl}
DF <- readr::read_csv( "../data-raw/20230212Cow01.csv",
                       col_types = list(vroom::col_integer(),
                                        #LineNo
                                        vroom::col_integer(),
                                        #Group
                                        vroom::col_character(),
                                        #Stage
                                        vroom::col_integer(),
                                        #cowCode
                                        vroom::col_character(),
                                        #cowGroup
                                        vroom::col_character(),
                                        #cowidNo
                                        vroom::col_date( format = "%Y/%m/%d" ),
                                        #birthday
                                        vroom::col_integer(),  #parity
                                        vroom::col_date( format = "%Y/%m/%d" ),
                                        #calving_date
                                        vroom::col_integer(),  #daysfrmcalving
                                        vroom::col_integer(),  #AItimes
                                        vroom::col_date( format = "%Y/%m/%d" ),
                                        #firstAI_date
                                        vroom::col_integer(),
                                        #fstAIdaysfrmcalving
                                        vroom::col_date( format = "%Y/%m/%d" ),
                                        #lastAI_date
                                        vroom::col_integer(),  #daysfrmlstAI
                                        vroom::col_date( format = "%Y/%m/%d" ),
                                        #expDateofnextCalving
                                        vroom::col_integer(),
                                        #opendays
                                        vroom::col_date( format = "%Y/%m/%d" )))
                                        #base_date

str(DF)
head(DF)

#str("../data/DF")
#head("../data/DF")

# 累計受胎率　=　(受胎頭数/(授精回数 - 妊否不明授精回数))*100(%)
#	　　ttlCR = (hsofPreg/(sNofAIs - sPUnkNofAIs)*100 %

#受胎頭数
hsofpreg <- hsofpreg(DF)
hsofpreg

#授精回数の合計
sofaitimes <- sofaitimes(DF)
sofaitimes

#妊否不明の授精回数
nofunkpr_ai <- nofunkpr_ai(DF)
nofunkpr_ai

#累計受胎率
ttlCR <- ttlcr(DF)
ttlCR

# 累計人工授精率 =  ((授精回数 - 妊不明の授精回数)/
#                         (サイクル数 - 妊不明のサイクル数))*100(%) 

#サイクル数の合計 VWP = 50
sofcycles <- sofcycles(DF, 50)
sofcycles

#妊不明サイクル数の合計
snofunkpr_cycles <- snofunkpr_cycles(DF, 50)
snofunkpr_cycles

#累計人工授精率(%)
ttlAIR <- ttlair(DF, 50)
ttlAIR

```
